**Results Template**

### 2021-10-21 3_inferential_questionnaire.Rmd
update lie and maia

---
output: html_document
editor_options: 
  chunk_output_type: console
---
## The effect of TOM ability on confidence and RT
### Yoni task
no correlation of yoni score with confidence
```{r}
model <- glmmTMB(DT_confidence ~ yoni_total + DT_RT + (1|ID) + (1|item), data = df)
parameters(model, effects = "fixed")
viz_data <- estimate_relation(model, at = "yoni_total")
ggplot(data = viz_data, aes(x = yoni_total, y = Predicted)) +
  geom_point(data = df.plot, aes(x = yoni_total, y = DT_confidence, color = ID), show.legend = FALSE) +
  geom_line() +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high), alpha = 0.3)
```

no correlation of yoni score with RT
```{r}
model <- glmmTMB(DT_RT ~ yoni_total + DT_confidence + (1|ID) + (1|item), data = df)
parameters(model, effects = "fixed")
viz_data <- estimate_relation(model, at = "yoni_total")
ggplot(data = viz_data, aes(x = yoni_total, y = Predicted)) +
  geom_point(data = df.plot, aes(x = yoni_total, y = DT_RT, color = ID), show.legend = FALSE) +
  geom_line() +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high), alpha = 0.3)
```

### BES
no correlation of BES score with confidence
```{r}
model <- glmmTMB(DT_confidence ~ BES_total + DT_RT + (1|ID) + (1|item), data = df)
parameters(model, effects = "fixed")
viz_data <- estimate_relation(model, at = "BES_total")
ggplot(data = viz_data, aes(x = BES_total, y = Predicted)) +
  geom_point(data = df.plot, aes(x = BES_total, y = DT_confidence, color = ID), show.legend = FALSE) +
  geom_line() +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high), alpha = 0.3)
```

no correlation of BES score with RT
```{r}
model <- glmmTMB(DT_RT ~ BES_total + DT_confidence + (1|ID) + (1|item), data = df)
parameters(model, effects = "fixed")
viz_data <- estimate_relation(model, at = "BES_total")
ggplot(data = viz_data, aes(x = BES_total, y = Predicted)) +
  geom_point(data = df.plot, aes(x = BES_total, y = DT_RT, color = ID), show.legend = FALSE) +
  geom_line() +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high), alpha = 0.3)
```

## The effect of interoceptive ability on confidence and RT
### HCT
no correlation of HCT accuracy with confidence
```{r}
model <- glmmTMB(DT_confidence ~ HCT_accuracy + DT_RT + (1|ID) + (1|item), data = df)
parameters(model, effects = "fixed")
viz_data <- estimate_relation(model, at = "HCT_accuracy")
ggplot(data = viz_data, aes(x = HCT_accuracy, y = Predicted)) +
  geom_point(data = df.plot, aes(x = HCT_accuracy, y = DT_confidence, color = ID), show.legend = FALSE) +
  geom_line() +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high), alpha = 0.3)
```

no correlation of HCT accuracy with RT
```{r}
model <- glmmTMB(DT_RT ~ HCT_accuracy + DT_confidence + (1|ID) + (1|item), data = df)
parameters(model, effects = "fixed")
viz_data <- estimate_relation(model, at = "HCT_accuracy")
ggplot(data = viz_data, aes(x = HCT_accuracy, y = Predicted)) +
  geom_point(data = df.plot, aes(x = HCT_accuracy, y = DT_RT, color = ID), show.legend = FALSE) +
  geom_line() +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high), alpha = 0.3)
```

### MAIA
the higher the MAIA the higher the confidence (p=0.048)
```{r}
model <- glmmTMB(DT_confidence ~ MAIA_total + DT_RT + (1|ID) + (1|item), data = df)
parameters(model, effects = "fixed")
viz_data <- estimate_relation(model, at = "MAIA_total")
ggplot(data = viz_data, aes(x = MAIA_total, y = Predicted)) +
  geom_point(data = df.plot, aes(x = MAIA_total, y = DT_confidence, color = ID), show.legend = FALSE) +
  geom_line() +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high), alpha = 0.3)
```

the higher the MAIA the lower the RT (p=0.035)
```{r}
model <- glmmTMB(DT_RT ~ MAIA_total + DT_confidence + (1|ID) + (1|item), data = df)
parameters(model, effects = "fixed")
viz_data <- estimate_relation(model, at = "MAIA_total")
ggplot(data = viz_data, aes(x = MAIA_total, y = Predicted)) +
  geom_point(data = df.plot, aes(x = MAIA_total, y = DT_RT, color = ID), show.legend = FALSE) +
  geom_line() +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high), alpha = 0.3)
```

```{r test}
model <- glmmTMB(DT_confidence ~ MAIA_total + DT_RT + (1|ID) + (1|item), data = df)
parameters(model, effects = "fixed")
viz_data <- estimate_relation(model, at = "MAIA_total")
ggplot(data = viz_data, aes(x = MAIA_total, y = Predicted)) +
  geom_boxplot(data = df, aes(x = MAIA_total, y = DT_confidence, color = ID), show.legend = FALSE) + 
  geom_line() +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high), alpha = 0.3)
```

## idea for within
independent variable: 
each participant is assigned a percentile for yoni/bes/hct/maia
objective-objective and subjective-subjective to obtain difference in TOM-int ability

dependent variable:
average of DT_confidence in social - polygraph
hmm

hypothesis: 
the higher the difference in TOM-int, the higher the social-polygraph confidence
(though this does not seem to be the case in descriptive)

>>>>

---
output: html_document
editor_options: 
  chunk_output_type: console
---
```{r}
plot_effect <- function(model, var) {
  viz_data <- estimate_relation(model, at = c("condition", var, "instruction"))
  ggplot(data = viz_data, aes_string(x = var, y = "Predicted")) +
    geom_point(data = df.plot, aes_string(y = "DT_confidence", color = "condition"), show.legend = FALSE) +
    geom_line(aes_string(color = "condition")) +
    geom_ribbon(aes_string(ymin = "CI_low", ymax = "CI_high", fill = "condition"), alpha = 0.3) + 
    facet_wrap(~instruction)
}
plot_effect(model, "MAIA_total")
```

## The effect of TOM ability on confidence and RT
### Yoni task
```{r}
model <- glmmTMB(DT_confidence ~ instruction/(condition*yoni_total) + (1|ID) + (1|item), data = df)
parameters(model, effects = "fixed")
viz_data <- estimate_relation(model, at = c("condition", "yoni_total", "instruction"))
ggplot(data = viz_data, aes(x = yoni_total, y = Predicted)) +
  geom_point(data = df.plot, aes(y = DT_confidence, color = condition), show.legend = FALSE) +
  geom_line(aes(color = condition)) +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high, fill = condition), alpha = 0.3) + 
  facet_wrap(~instruction)
```
the higher someone scores in yoni, the bigger the difference in lie and truth

### BES
```{r}
model <- glmmTMB(DT_confidence ~ instruction/(condition*BES_total) + (1|ID) + (1|item), data = df)
parameters(model, effects = "fixed")
viz_data <- estimate_relation(model, at = c("condition", "BES_total", "instruction"))
ggplot(data = viz_data, aes(x = BES_total, y = Predicted)) +
  geom_point(data = df.plot, aes(y = DT_confidence, color = condition), show.legend = FALSE) +
  geom_line(aes(color = condition)) +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high, fill = condition), alpha = 0.3) + 
  facet_wrap(~instruction)
```

## The effect of interoceptive ability on confidence and RT
### HCT
```{r}
model <- glmmTMB(DT_confidence ~ instruction/(condition*HCT_accuracy) + (1|ID) + (1|item), data = df)
parameters(model, effects = "fixed")
viz_data <- estimate_relation(model, at = c("condition", "HCT_accuracy", "instruction"))
ggplot(data = viz_data, aes(x = HCT_accuracy, y = Predicted)) +
  geom_point(data = df.plot, aes(y = DT_confidence, color = condition), show.legend = FALSE) +
  geom_line(aes(color = condition)) +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high, fill = condition), alpha = 0.3) + 
  facet_wrap(~instruction)
```

### MAIA
```{r}
model <- glmmTMB(DT_confidence ~ instruction/(condition*MAIA_total) + (1|ID) + (1|item), data = df)
parameters(model, effects = "fixed")
parameters(emmeans::emtrends(model, ~instruction, var = "MAIA_total")) # main effect only significant for lie, averages (properly) over condition -> similar to instruction/MAIA_total but takes into account condition
```

### 2021-10-21 scripts/claudia/data processing.Rmd
update lie and maia

  mutate(MAIA1 = (Q1+Q2+Q3+Q4)/4, MAIA2 = (Q5+Q6+Q7+Q8+Q9+Q10)/6, MAIA3 = (Q11+Q12+Q13+Q14+Q15)/5, MAIA4 = (Q16+Q17+Q18+Q19+Q20+Q21+Q22)/7,
        MAIA5 = (Q23+Q24+Q25+Q26+Q27)/5, MAIA6 = (Q28+Q29+Q30+Q31)/4, MAIA7 = (Q32+Q33+Q34)/3, MAIA8 = (Q35+Q36+Q37)/3) %>% 
  mutate(MAIA_total = (MAIA1+MAIA2+MAIA3+MAIA4+MAIA5+MAIA6+MAIA7+MAIA8)/8) %>%

@@

@@

# write.csv(results, file = "Lie Scale_processed.csv", row.names=FALSE)
```

>>>>

  mutate(MAIA1 = (Q1+Q2+Q3+Q4)/4, MAIA2 = (Q5+Q6+Q7+Q8+Q9+Q10)/6, MAIA3 = (Q11+Q12+Q13+Q14+Q15)/5, MAIA4 = (Q16+Q17+Q18+Q19+Q20+Q21+Q22)/7,
        MAIA5 = (Q23+Q24+Q25+Q26+Q27)/5, MAIA6 = (Q28+Q29+Q30+Q31)/4, MAIA7 = (Q32+Q33+Q34)/3, MAIA8 = (Q35+Q36+Q37)/3) %>% 
  mutate(MAIA_total = (MAIA1+MAIA2+MAIA3+MAIA4+MAIA5+MAIA6+MAIA7+MAIA8)/8) %>%
  rename(MAIA_noticing = MAIA1,
         MAIA_not_distracting = MAIA2,
         MAIA_not_worrying = MAIA3,
         MAIA_attention_regulation = MAIA4,
         MAIA_emotional_awareness = MAIA5,
         MAIA_self_regulation = MAIA6,
         MAIA_body_listening = MAIA7,
         MAIA_trusting = MAIA8) %>%

@@

  mutate(lie_ability = (Q4+Q5+Q6+Q7)/4, 
         lie_frequency = (Q1+Q2+Q3+Q8)/4, 
         lie_negativity = (Q9+Q11+Q13+Q16)/4, 
         lie_contextuality = (Q10+Q12+Q14+Q15)/4) %>%

@@

write.csv(results, file = "liescale_processed.csv", row.names=FALSE)
```
